### 2018-01-04 manuscript.rmd
fixed another citation in the rmd, did not rebuild pdf
updated with paper citation and docker image link

KMRR considered several publicly available datasets of gene expression across tissues and species. Their expression summary statistic is tau [@Yanai:2005dh, @KryuchkovaMostacci:2016in], an indicator of tissue specificity of gene expression. Tau can range from a value of 0, which indicates no specificity (*i.e.*, uniform expression across tissues), to a value of 1, which indicates high specificity (*i.e.*, expression in only one tissue). Tau is convenient in that it is a single number of defined range for each gene, though of course since the original expression is multidimensional this means much information is discarded. This includes information about which tissue expression is specific to. For example, if one gene has expression specific to the brain and another expression specific to the kidney, both would have a tau of 1.

@@

To test the hypothesis that ancient duplications that precede the oldest speciation event (*SI Appendix*, Fig. S5*A*) impact the lower correlation of tau between paralogs than between orthologs, we removed them. When we consider only the duplication events the same age or younger than the oldest speciation event (*SI Appendix*, Fig. 5*B*), the paralog correlation coefficient increases from `r signif( paralog_r$estimate, 2)` to `r signif( paralog_subset_r$estimate, 2)` ($P`r format_p(paralog_subset_r)`$). This is much closer to the ortholog correlation of `r signif( ortholog_r$estimate, 2) `.

@@

We fit BM and OU models for the evolution of tau on each gene tree with the R package geiger [@Pennell:2014jf]. This produced parameter estimates and AIC scores, $AIC_{BM}$ and $AIC_{OU}$, for each tree for each model. For each tree, we then calculated the AIC differences $\Delta AIC$ for each model as $\Delta AIC_{BM}=AIC_{BM}-min(AIC_{BM}, AIC_{OU})$ and $\Delta AIC_{OU}=AIC_{OU}-min(AIC_{BM}, AIC_{OU})$. The lower the $\Delta AIC$ for a model, the more plausible it is. $\Delta AIC<2$ is generally regarded as substantial relative support for a model. If multiple models have a low $\Delta AIC$, then there is little difference in the plausibility of the models. Since we are only considering two models, for each gene tree either $\Delta AIC_{BM}$ or $\Delta AIC_{OU}$ (or both) will be $0$.

>>>>

KMRR considered several publicly available datasets of gene expression across tissues and species. Their expression summary statistic is tau [@Yanai:2005dh; @KryuchkovaMostacci:2016in], an indicator of tissue specificity of gene expression. Tau can range from a value of 0, which indicates no specificity (*i.e.*, uniform expression across tissues), to a value of 1, which indicates high specificity (*i.e.*, expression in only one tissue). Tau is convenient in that it is a single number of defined range for each gene, though of course since the original expression is multidimensional this means much information is discarded. This includes information about which tissue expression is specific to. For example, if one gene has expression specific to the brain and another expression specific to the kidney, both would have a tau of 1.

@@

To test the hypothesis that ancient duplications that precede the oldest speciation event (*SI Appendix*, Fig. S3*A*) impact the lower correlation of tau between paralogs than between orthologs, we removed them. When we consider only the duplication events the same age or younger than the oldest speciation event (*SI Appendix*, Fig. S3*B*), the paralog correlation coefficient increases from `r signif( paralog_r$estimate, 2)` to `r signif( paralog_subset_r$estimate, 2)` ($P`r format_p(paralog_subset_r)`$). This is much closer to the ortholog correlation of `r signif( ortholog_r$estimate, 2) `.

@@

We fit BM and OU models for the evolution of tau on each gene tree with the R package geiger [@Pennell:2014jf]. This produced parameter estimates and AIC scores, $AIC_{BM}$ and $AIC_{OU}$, for each tree for each model. For each tree, we then calculated the AIC differences $\Delta AIC$ for each model as $\Delta AIC_{BM}=AIC_{BM}-min(AIC_{BM}, AIC_{OU})$ and $\Delta AIC_{OU}=AIC_{OU}-min(AIC_{BM}, AIC_{OU})$. The lower the $\Delta AIC$ for a model, the more plausible it is. $\Delta AIC<2$ is generally regarded as substantial relative support for a model. If multiple models have a low $\Delta AIC$, then there is little difference in the plausibility of the models. Since we are only considering two models, for each gene tree either $\Delta AIC_{BM}$ or $\Delta AIC_{OU}$ will be $0$.
